---
title: "kennycho-peercommentary-inovick"
output: html_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
install.packages("stringr")
library("stringr")

```

## Peer Commentary

## Challenge 1
```{r}

v1 <- c("Stately", "plump", "Buck", "Mulligan", "came", "from", "the", "stairhead,", "bearing", "a", "bowl", "of", "lather", "on", "which", "a", "mirror", "and", "a", "razor", "lay", "crossed")
v1

v1[seq(from = 1, to = 100, by = 3)]
str_split(v1)

 
```

## Error 1: unmatched opening bracket, however, it is matched, so I'm not sure what the problem is. Something is weird with this syntax. PLus signs are happening in the console
## Comment: to in sequence v1 could simply be the length of v1, instead of 100. I might be incorrect about this, but I believe sequencing to 100 is both inefficient and creates null memory slots? Something along those lines. Str_split() has no spllit parameter.

## Challenge 2
## Comment: First extraction is not in the module, but it is not a problem. Your method of extracting specific columns and rows is better than mine. 
```{r}
m <- matrix(data = 1:80, nrow = 8, ncol = 10, byrow = FALSE)
m
x <- m[4, 5]
x
#1st step, extracting columns 2, 3, and 6 and assigning them to variable x
x1 <- m[,c(2,3,6)] 
x1
#2nd step, extracting rows 6 and 8
x2 <- m[c(6,8),] 
x2
#3rd step, extracting rows and columns
x3 <- m[c(2:6), c(2:9)]
x3
```

## Challenge 3
```{r}
a <- array(data = 400:1, dim = c(5, 5, 4, 4))
a

#1st step
a[1, 1, 1, 2]

#2nd step
a[2, 3, 2, ]

#3rd step
a[1:5, 1:5, 3, 3]
```
```{r}
Platyrrhini <- c("Cebidea", "Atelidae", "Pitheciidae")
Catarrhini <- c("Cercopithecidea", "Hylobatidae", "Hominidae")
Anthropoidea <- list(Platyrrhini, Catarrhini)
names(Anthropoidea) <- list("Platyrrhini", "Catarrhini")
Anthropoidea
Tarsioidea <- c("Tarsiidae")
Haplorhini <- list(Anthropoidea, Tarsioidea)
names(Haplorhini) <- list("Anthropoidea", "Tarsioidea")
Haplorhini
Lorisoidea <- c("Lorisidae", "Galagidae")
Lemuroidea <- c("Cheirogaleidae", "Lepilemuridae", "Indriidae", "Lemuridae", "Daubentoniidae")
Strepsirhini <- list(Lorisoidea, Lemuroidea)
names(Strepsirhini) <- list("Lorisoidea", "Lemuroidea")
Strepsirhini
Primates <- list(Haplorhini, Strepsirhini)
names(Primates) <- list("Haplorhini", "Strepsirhini")
Primates
```
## Error2: More syntax problems, more unexpected tokens. It still ran but it doesn't like the commas, quotation marks or brackets.

## Challenge 5
## Comment: Should be good, assuming my understanding of data frames and str() is correct.
```{r}
m3 <- matrix(data = c(3, 0, 1 ,23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2), nrow = 5, ncol = 3, byrow = TRUE)
m3
m3.df <- as.data.frame(t(m3))
as.logical(m3.df$Col2)
as.factor(m3.df$Col3)
str(m3.df)
```